Poster Data Analysis

### 2018-09-09 notebooks/poster_analysis.Rmd
added correlation plot for MIC's

```{r, include = FALSE}
# Libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, ggplot2, tidyr, cowplot, viridis, forcats)

@@

## MIC plot

```{r message=FALSE, warning=FALSE}
selected_genes <- c("qnrA1","qnrB19","qnrB6","qnrB60","qnrS1","qnrS2","qnrS4")
selected_mut <- c("gyrA","gyrB","parC","parE","marR")

@@

>>>>

```{r, include = FALSE}
# Libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr, ggplot2, tidyr, cowplot, viridis, forcats, radiant.data)

@@

## MIC plots

### MIC Distribution for generated groups
```{r message=FALSE, warning=FALSE}
selected_genes <- c("qnrA1","qnrB19","qnrB6","qnrB60","qnrS1","qnrS2","qnrS4")
selected_mut <- c("gyrA","gyrB","parC","parE","marR")

@@

### MIC correlation plots per animal species

```{r}
test <- mic_data %>%
  select(-antres) %>%
  left_join(species_data, by = "id") %>%
  mutate(SMX_R = ifelse(SMX > 64, 1, 0),
         TMP_R = ifelse(TMP > 2, 1, 0),
         CIP_R = ifelse(CIP > 0.06, 1, 0),
         TET_R = ifelse(TET > 8, 1, 0),
         NAL_R = ifelse(NAL > 16, 1, 0),
         CTX_R = ifelse(CTX > 0.25, 1, 0),
         CHL_R = ifelse(CHL > 16, 1, 0),
         AMP_R = ifelse(AMP > 8, 1, 0),
         GEN_R = ifelse(GEN > 2, 1, 0)) %>%
  select(contains("_R"), species) %>%
  split(., f = .$species) %>%
  lapply(., function(x) select(x, -species))

create_corr_matrix <- function(df) {
  df <- df %>%
    as.matrix %>%
    cor %>%
    as.data.frame %>%
    rownames_to_column(var = "var1") %>%
    gather(var2, value, -var1) %>%
    mutate(var1 = gsub("(.*?)_R$", "\\1", var1),
           var2 = gsub("(.*?)_R$", "\\1", var2))
  return(df)
}

corr_matrices <- lapply(test, function(x) create_corr_matrix(x)) %>%
  bind_rows(.id = "species")

cols <- c("#e7f0fa","#c9e2f6","#95cbee","#0099dc","#4ab04a", "#ffd73e","#eec73a","#e29421","#f05336","#ce472e")

ggplot(corr_matrices, aes(var1, var2, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradientn(colors=cols,
                       na.value="grey95",
                       limits=c(-1, 1),
                       guide=guide_colourbar(ticks=T,nbin=10,
                                             barheight=.5,label=T, 
                                             barwidth=10))+
  labs(fill = NULL)+
  theme_classic()+
  theme(axis.text = element_text(size = 7),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4),
        axis.title = element_blank(),
        legend.position="bottom",
        legend.justification="center",
        legend.direction="horizontal")+
  coord_fixed()+
  facet_wrap(~species)
```
